Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-03-13 paper/ms.tex
Finished adding updates to section 1.

\subsection{Proposed Progenitor Settings}

@@

Modern computing resources now enable simulations with unprecedented
realism, allowing both one-dimensional simulations with a vast
amount of included physics and full three-dimensional simulations
albeit with less included physics~\citep{caldertownsley2018}.
In the area of stellar evolution, recent investigations revisiting
late-time evolution of roughly 8 \Msun stars indicate that under
the right circumstances, ``hybrid" white dwarfs having a C/O core surrounded by O/Ne
mantle may form \citep{siess2009,denissenkovetal2013}. These hybrid
white dwarf are thought to form when mixing at the lower convective boundary quenches
C burning in an asymptotic giant branch (AGB) star, leaving unburned C
in the core. The situation is at best uncertain, however, and the
results depending on assumptions about convective
overshoot that have been questioned \citep{chenetal2014,lecoanetetal16,lattanzioetal2017}.

A hybrid WD can become a progenitor of a thermonuclear supernova via two
of the progenitor system.
First, the hybrid could be part of a binary system in which the companion star becomes
another white dwarf and the two merge. Recent population synthesis work supports
this pathway by indicating a substantial contribution to the Ia population rate from
mergers where one member is a hybrid~\citep{yungelsonkuranov2017}. Second, if the hybrid
WD is part of a binary with a main sequence or giant companion, it can gain mass and
approach the Chandrasekhar mass, i.e.\  the single degenerate picture~\citep{willcoxetal2016}.
{\color{red} COULD NOT FIND ANY EVIDENCE OF HYBRIDS IN THE SUBCHANDRA PATH. SAY
SOMETHING?}

In either {\color{red}ANY} case, the hybrid WD will experience a period of cooling, which will
make the core-mantle interface subject to convective
instability \citep{brooksetal2017,schwabgaraud2018}. In the case of the
hybrid WD accreting and approaching the Chandrasekhar mass, accretion will
heat the core and start C fusion, leading to a period of ``simmering" prior
to the explosion \citep{PiroBild08}. The upshot is that is likely to be considerable
mixing after the hybrid forms that may homogenize the composition
\citep{denissenkovetal2015,brooksetal2017,schwabgaraud2018}.

@@

From population synthesis, \citet{mengpods2014} found that these
%meng received may 5 accepted may 16
progenitors may substantially contribute to the population of \SNeIa (1-8\%) and have
relatively short delay times. They also suggested that these
may produce part of the Iax class of events. \citet{Wangetal2014} also with population
synthesis studied the case
%received august 28 accepted sept 26
of a hybrid progenitor accreting from a non-degenerate He star and found
birth rates indicating that up to 18\% of SNe Ia may follow from this channel
and very short delay times. \citet{Wangetal2014} also suggested that explosions
from hybrid progenitors may provide an explanation for type Iax events.
\citet{mengpods2018}, from the common-envelope-wind model developed in
\citep{mengpods2014}, propose that both Ia-CSM and Iax events
are caused by the explosion of hybrid progenitors, with Ia-CSM occurring in systems with
a massive common envelope and Iax events occurring in systems where most of the common envelope
has been lost.

Other groups have simulated explosions from hybrid progenitors.
\citet{kromeretal2015} performed pure deflagration simulations from models
with a C core. They found that their models may explain some faint events
such as SN 2008ha~\citep{foleyetal2009}.
\citet{bravoetal2016} performed one-dimensional simulations of explosions from
a variety of progenitor models assuming both pure deflagration and the DDT
explosion mechanism.
Some of their models are similar to those of \citep{denissenkovetal2015} and
they report that many models produce less synthesized
\Ni{56}, indicating dimmer events. They also note that some of their
models may explain Iax events.
\citet{willcoxetal2016} simulated explosions from the progenitors of
\citep{denissenkovetal2015} and found a trend of lower energy and lower
\Ni{56} yield when compared to explosions from traditional C/O progenitors.

>>>>

\subsection{Proposed Progenitor Settings}\label{sec:progenitors}

@@

Modern computing resources now enable simulations with unprecedented
realism, allowing both one-dimensional simulations with a vast
amount of included physics and full three-dimensional simulations
albeit with less included physics~\citep{caldertownsley2018}.
In the area of stellar evolution, recent investigations revisiting
late-time evolution of roughly 8 \Msun~stars indicate that under
the right circumstances, ``hybrid" white dwarfs having a C/O core surrounded by O/Ne
mantle may form \citep{siess2009,denissenkovetal2013}. These hybrid
white dwarfs are thought to form when mixing at the lower convective boundary quenches
C burning in an asymptotic giant branch (AGB) star, leaving unburned C
in the core. The situation is at best uncertain, however, and the
results depend on assumptions about convective
overshoot that have been questioned {\color{blue} [questioned for what reasons?]} \citep{chenetal2014,lecoanetetal16,lattanzioetal2017}.

A hybrid WD can become a progenitor of a thermonuclear supernova via two
of the progenitor scenarios discussed in Section \ref{sec:progenitors}.
First, the hybrid could be part of a binary system in which the companion star becomes
another white dwarf and the two merge. Recent population synthesis work supports
this pathway by indicating a substantial contribution to the Ia population rate from
mergers where one member is a hybrid~\citep{yungelsonkuranov2017}. Second, if the hybrid
WD is part of a binary with a main sequence or giant companion, it can gain mass and
approach the Chandrasekhar mass, i.e.\  the single degenerate picture~\citep{willcoxetal2016}.
{\color{red} COULD NOT FIND ANY EVIDENCE OF HYBRIDS IN THE SUBCHANDRA PATH. SAY
SOMETHING?}

In either {\color{red}ANY} case, the hybrid WD will experience a period of cooling, which will
make the core-mantle interface subject to convective
instability \citep{brooksetal2017,schwabgaraud2018}.
{\color{blue} [can we say a bit more about how this cooling-caused instability works?]}
In the case of the
hybrid WD accreting and approaching the Chandrasekhar mass, accretion will
heat the core and start C fusion, leading to a period of ``simmering" prior
to the explosion \citep{PiroBild08}. The upshot is that there is likely to be considerable
mixing after the hybrid forms that may homogenize the composition
\citep{denissenkovetal2015,brooksetal2017,schwabgaraud2018}.

@@

From population synthesis, \citet{mengpods2014} found that these
%meng received may 5 accepted may 16
progenitors may substantially contribute to the population of \SNeIa\ (1-8\%) and have
relatively short delay times. They also suggested that these
may produce part of the Iax class of events. \citet{Wangetal2014} also with population
synthesis studied the case
%received august 28 accepted sept 26
of a hybrid progenitor accreting from a non-degenerate He star and found
birth rates indicating that up to 18\% of SNe Ia may follow from this channel
and very short delay times. \citet{Wangetal2014} also suggested that explosions
from hybrid progenitors may provide an explanation for type Iax events.
\citet{mengpods2018}, from the common-envelope-wind model developed in
\citet{mengpods2014}, propose that both Ia-CSM and Iax events
are caused by the explosion of hybrid progenitors, with Ia-CSM occurring in systems with
a massive common envelope and Iax events occurring in systems where most of the common envelope
has been lost.

Other groups have simulated explosions from hybrid progenitors.
\citet{kromeretal2015} performed pure deflagration simulations from models
with a C core. They found that their models may explain some faint events
such as SN 2008ha~\citep{foleyetal2009}.
\citet{bravoetal2016} performed one-dimensional simulations of explosions from
a variety of progenitor models assuming both pure deflagration and the DDT
explosion mechanism.
Some of their models are similar to those of \citep{denissenkovetal2015} and
they report that many models produce less synthesized
\Ni{56}, indicating dimmer events. They also note that some of their
models may explain Iax events.
\citet{willcoxetal2016} simulated explosions from the progenitors of
\citet{denissenkovetal2015} and found lower
\Ni{56} yields on average and a trend of lower ejecta kinetic energy
when compared to explosions from traditional C/O progenitors.
